The imprint of global magma oceans on exoplanet demographics

### 2023-01-30 src/tex/ms.tex
comment on M dwarf rgh phases

    Our tests with different spectral types (Sect.~\ref{sec:results_FGK_M}) show that the information content of M~dwarfs in a sample dominates the hypothesis tests.
The reason is, besides their large number in a volume/magnitude-limited sample, that many detected M~dwarf planets are located near the threshold instellation.
As in the cases above, an M~dwarf survey profits from follow-up measurements of planetary masses with an order of magnitude increase in evidence.
\end{note}

>>>>

    Our tests with different spectral types (Sect.~\ref{sec:results_FGK_M}) show that the information content of M~dwarfs in a sample dominates the hypothesis tests.
The reason is, besides their large number in a volume/magnitude-limited sample, that many detected M~dwarf planets are located near the threshold instellation.
As in the cases above, an M~dwarf survey profits from follow-up measurements of planetary masses with an order of magnitude increase in evidence.

    An additional advantage of targeting M~dwarfs are their extended runaway greenhouse phases, whose duration can reach the order of \SI{100}{\mega\year}~CITE.
    This increases the probability of observing any given planet in the sample during the runaway greenhouse phase, essentially driving $f_\mathrm{rgh}$ to higher values.
\end{note}
